---
title: "Bayesian Optimization for Nanotopography exploration"
output: github_document
---

This notebook shows results for optimizing Topography with respect to osteogenesis, but can be easily altered to use the morphome by changing the input data set. 

Notes specifically for Bayesian optimization protocol/algorithm:
- Topography data is mean centered and scaled (mean = 0, sd=1)
- Note that Y data we are trying to optimize is just the weighted sum of bone gene expression, normalized to (0,1] by dividing by the maximum across 2 replicates
- SQ AND HEX SEPARATED WITH THE ANGLES REMOVED FROM THE SEARCH!!
- Uses averaage of PCR data per replicate
- Nanotopography parameters being explored: Diameter and Disorder (Angles not Included, geometry modelled separately!)
- The GP model used in the Bayesian optimization does not have the optimizer
- The random search was performed by just getting a random datapoint within the available dataset, but the maximum Y is computed from a GP model using the random dataset

Call functions needed from R
```{r message=FALSE, warning=FALSE}
library(reticulate)
library(ggplot2)
library(tidyverse)
library(caret)
library(tidyverse)
library(reshape2)
library(glue)
library(brms)
library(dplyr)
use_condaenv(condaenv = 'python36', required = TRUE)
```

Import the datasets that we need and process them as needed. Here we use the topography parameters disorder and diameter (scaled by geometry to have mean = 0 and standard deviation = 1), but this can be easily changed to use morphome features. Additionally, the dataset that we import already has the weighted sum of osteogenic genes RUNX2, OSX, OCN and OPN
```{r message=FALSE, warning=FALSE}
#data import
#choose which data to perform Bayesian optimization on
allData <- read_csv("meanBayesOptData_noFlat.csv")
#DISORDER AND DIAMETER DATA USED IS SCALED BY GEOMETRY

```

Get a baseline Gaussian process model using the entire dataset with an initialized RBF*Constant Kernel. Data is split 60-40 train-test. GP regression performed without optimizer
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#perform a gp regression to show that we can do it with the current dataset
rm('gp_modeling_split.py')
source_python('gp_modeling_split.py')

for (g in 1:2){
   geomData <- subset(allData, allData$Geometry_Number == g)
   x = as.data.frame(geomData[,7:8])
   yraw = as.data.frame(geomData[,14:17])
   ylog = log(yraw, 10)
   ymax = unlist(lapply(ylog, max))
   y = ylog/ymax
   topotopcr_model_base <- gp_modeling_split(x=x, y=y)
   assign(glue("topotopcr_model_base_geom{g}"), topotopcr_model_base)
   assign(glue("x_geom_{g}"), x)
   assign(glue("y_geom_{g}"), ylog)
   
   #to get initial values for the kernel
   kern_bayesopt <- topotopcr_model_base[[9]]
   kern_rnd <- topotopcr_model_base[[9]]
   
   assign(glue("kern_bayesopt_{g}"), kern_bayesopt)
   assign(glue("kern_rnd_{g}"), kern_rnd)
 }

```


Plot of the GP regression
```{r}
ypred <- NULL
yactual <- NULL
geometryHolder <- NULL
ydata <- NULL

for(g in 1:2){
   gpModelToUse<-get(glue("topotopcr_model_base_geom{g}"))
   ypred<-  unlist(gpModelToUse[[6]])
   names(ypred)[1] <- "train"
   yactual <- unlist(gpModelToUse[[8]])
   names(yactual)[1] <- "test"
   ydataHolder <- as.data.frame(cbind(ypred, yactual))
   ydataHolder$geometry <- g
   ydata <- rbind(ydata, ydataHolder)
}

   ggplot(ydata, aes(x=ypred, y=yactual)) + geom_point() + geom_abline(color="red") + 
      facet_wrap(~geometry) +
      labs(x="predicted qPCR value", y="actual qPCR value")
   
```

Bayesian Optimization Scenario 1. Let's try to see if the Bayesian Optimization protocol can be used to more efficiently sample the topography space to maximize PCR. Recall that for Bayesian optimization, we only use the weighted sum of Genes4-Genes7 (single objective optimization).
```{r message=FALSE, warning=FALSE, collapse=TRUE}
rm('bayesian_optimization_nogrid')
source_python('bayesian_optimization_real_noGrid2.py')

#set some parameters here
exp = 50
offset = 5
all_ymax_bayesopt <- NULL
all_ymax_rnd <- NULL
all_ind_bayesopt <- NULL
all_ind_rnd <- NULL
all_experiment <- NULL
all_iterations <- NULL


for (g in 1:2){
   geomData <- subset(allData, allData$Geometry_Number == g)
   x = as.data.frame(geomData[,7:8])
   yraw = as.data.frame(geomData[,265])
   ylog = log10(yraw)
   ymax = unlist(lapply(ylog, max))
   y = ylog/ymax
   allTopoToPcr_s1 <- NULL
   indexBayesOptMax_s1 <- NULL 
   indexRndMax_s1 <- NULL
   
   maxiter = nrow(x)-1
   
   for (num in 1:exp){
      
    i=1
    set.seed(num*181+1938)
    ind_bayesopt = list(sample(1:nrow(x)-1, 1, replace=F))
    ind_rnd = list(sample(1:nrow(x)-1, 1, replace=F))
    all_ymax_bayesopt <- y[unlist(ind_bayesopt)+1,]
    all_ymax_rnd <- y[unlist(ind_rnd)+1,]
    active_ind_bayesopt <- ind_bayesopt
    active_ind_rnd <- ind_rnd
    all_iterations <- i
    all_experiment <- num
    
    kern_bayesopt <- get(glue("kern_bayesopt_{g}"))
    kern_rnd <- get(glue("kern_rnd_{g}"))
    
      for (i in 1:maxiter){
         res <- bayesian_optimization_nogrid(x=x, y=y, ind_active_bayesopt=active_ind_bayesopt, ind_active_rnd=active_ind_rnd, kernel_bayesopt=kern_bayesopt, n_offset_bayesopt=offset, iter=i)
   
         active_ind_bayesopt <- rbind(active_ind_bayesopt, unlist(res[[3]]))
         active_ind_rnd <- rbind(active_ind_rnd, unlist(res[[4]]))
         ind_bayesopt <- rbind(ind_bayesopt, unlist(res[[3]]))
         ind_rnd <- rbind(ind_rnd, unlist(res[[4]]))
         y_best_bayesopt_iter <- res[[5]]
         y_best_rnd_iter <- res[[6]]
         kern_bayesopt <- res[[7]]
         all_ymax_bayesopt <- rbind(all_ymax_bayesopt, unlist(y_best_bayesopt_iter))
         all_ymax_rnd <- rbind(all_ymax_rnd, unlist(y_best_rnd_iter))
         all_experiment <- rbind(all_experiment, num)
         all_iterations <- rbind(all_iterations, i)
   
      }
   holder <- bind_cols(ymax_bayesopt = all_ymax_bayesopt, ymax_rnd = all_ymax_rnd, chosen_bayesopt_index = unlist(ind_bayesopt), chosen_rnd_index = unlist(ind_rnd), experiment = all_experiment, iterations = all_iterations)
   holder$geometry <- g
   allTopoToPcr_s1 <- rbind(allTopoToPcr_s1, holder)
   print(paste0("Experiment Number:", num))
   indexBayesOptMax_s1 <- rbind(indexBayesOptMax_s1,  min(which(holder$ymax_bayesopt == max(holder$ymax_bayesopt))))
   indexRndMax_s1 <- rbind(indexRndMax_s1,  min(which(holder$ymax_rnd == max(holder$ymax_rnd))))
}
   assign(glue("res_geom{g}"), res)
   assign(glue("allTopoToPcr_s1_geom{g}"), allTopoToPcr_s1)
   assign(glue("indexBayesOptMax_s1_geom{g}"), indexBayesOptMax_s1)
   assign(glue("indexRndMax_s1_geom{g}"), indexRndMax_s1)
   
}
allTopoToPcr_s1 <- NULL
allTopoToPcr_s1 <- bind_rows(allTopoToPcr_s1_geom1, allTopoToPcr_s1_geom2)
indexBayesOptMax_s1 <- rbind(indexBayesOptMax_s1_geom1, indexBayesOptMax_s1_geom2)
indexRndMax_s1 <- rbind(indexRndMax_s1_geom1, indexRndMax_s1_geom2)

write.csv(allTopoToPcr_s1, file="allTopoToPcr_s1_combGeom.csv")
write.csv(indexBayesOptMax_s1, file="indexBayesOptMax_s1_combGeom.csv")
write.csv(indexRndMax_s1, file="indexRndMax_s1_combGeom.csv")

allTopoToPcr_s1$ExptGeomCombo <- paste0(allTopoToPcr_s1$geometry, sep="_", allTopoToPcr_s1$experiment)
allTopoToPcr_s1$ExptGeomComboArrange <- factor(allTopoToPcr_s1$ExptGeomCombo, levels=c("1_1", "1_2", "1_3", "1_4", "1_5", "2_1", "2_2", "2_3", "2_4", "2_5"))

meltDataYmax <- melt(allTopoToPcr_s1[c(1,2,6,7,9)], value.name = "ymax", variable.name = "type", id.vars=c("geometry", "ExptGeomComboArrange", "iterations"))

averageData <- meltDataYmax %>% 
    group_by(iterations, type, geometry) %>% 
    summarise(mean.value=mean(ymax), stdev.value = sd(ymax))

ggplot(averageData, aes(x = iterations, y = mean.value, color = type)) + 
   facet_wrap(~geometry, scales="free") +
   geom_errorbar(aes(ymin = mean.value - stdev.value, ymax = mean.value + stdev.value), alpha=0.5) + 
   geom_point() + 
   geom_line() +
   theme_bw() +
   labs(title="Bayesian optimization to demonstrate efficiency of getting optimum \n of known dataset (Scenario 1) \n averaged across 50 iterations", 
        x = "Experiments (Number of topographies queried)", 
        y = "Maximum qPCR value")

```

Lets find out how many iterations are needed on average to obtain the maximum using Bayesian optimization and the random search
```{r}
for (g in 1:2){
   averageDataSubset <- subset(averageData, averageData$geometry == g)
   yMaxIndex<-which(averageDataSubset$mean.value==max(averageDataSubset$mean.value))
   BayesOptMaxIndex <- averageDataSubset[min(yMaxIndex[lapply(yMaxIndex, "%%", 2)!=0]), 1]
   RndMaxIndex <- averageDataSubset[min(yMaxIndex[lapply(yMaxIndex, "%%", 2)==0]), 1]
   print(glue("Max iterations needed by Bayes Opt to get to optimum of geometry {g} is {BayesOptMaxIndex}"))
   print(glue("Max iterations needed by Rnd to get to optimum of geometry {g} is {RndMaxIndex}"))
}
```

What are the diameter and disorder measurements that correspond to the osteogenic maximum? Do they match the expected values of maximum, which is the NSQ-1um and HEX-1um? Yes they do!
```{r}
geomData_geom1 <- subset(allData, allData$Geometry_Number == 1)
geomData_geom2 <- subset(allData, allData$Geometry_Number == 2)
predictedgeom1_all_s1 <- NULL
predictedgeom2_all_s1 <- NULL

for(num in 1:exp){
   s4Subset_geom1 <- subset(allTopoToPcr_s1, allTopoToPcr_s1$experiment==num & allTopoToPcr_s1$geometry == 1)
   s4Subset_geom2 <- subset(allTopoToPcr_s1, allTopoToPcr_s1$experiment==num & allTopoToPcr_s1$geometry == 2)
   index_geom1 <- min(which(s4Subset_geom1$ymax_bayesopt == max(s4Subset_geom1$ymax_bayesopt)))
   index_geom2 <- min(which(s4Subset_geom2$ymax_bayesopt == max(s4Subset_geom2$ymax_bayesopt)))
   gridIndx_geom1 <- s4Subset_geom1[index_geom1,3]
   gridIndx_geom2 <- s4Subset_geom2[index_geom2,3]
   topo_geom1 <- geomData_geom1[gridIndx_geom1[[1]],]
   topo_geom2 <- geomData_geom2[gridIndx_geom2[[1]],]
   rescale_topo_geom1 <- bind_cols(Disorder = topo_geom1[,7]*335.19+200, Diameter = topo_geom1[,8]*736.36+811.11)
   rescale_topo_geom2 <- bind_cols(Disorder = topo_geom2[,7]*221.81+129.09, Diameter = topo_geom2[,8]*582.62+390.91)
   predictedgeom1_all_s1 <- rbind(predictedgeom1_all_s1, rescale_topo_geom1)
   predictedgeom2_all_s1 <- rbind(predictedgeom2_all_s1, rescale_topo_geom2)
}

print(glue("For HEX geometry, max topography have disorder {unique(predictedgeom1_all_s1[[1]])} and diameter {unique(predictedgeom1_all_s1[[2]])}"))
   print(glue("For SQ geometry, max topography have disorder {unique(predictedgeom2_all_s1[[1]])} and diameter {unique(predictedgeom2_all_s1[[2]])}"))
   
```


Next, we use Gaussian Process (GP) regression to create a model that predicts individual PCR values using the topography parameters. GP regression is performed with train and test sets, validation performed using test set.
```{python}
import numpy as np
import sklearn.gaussian_process as gp
from copy import deepcopy
import pandas as pd

trainsize1 = int(0.9*len(r.x_geom_1))
testsize1 = int(len(r.x_geom_1)-trainsize1)
indices1   = np.random.permutation(np.size(r.x_geom_1,axis=0))
ind_train1 = np.sort(indices1[0:trainsize1,])
ind_test1  = np.sort(indices1[testsize1:,])
x_train_geom1= r.x_geom_1.iloc[ind_train1,0:len(r.x_geom_1.columns)]
x_test_geom1 = r.x_geom_1.iloc[ind_test1,0:len(r.x_geom_1.columns)]
y_train_geom1= r.y_geom_1.iloc[ind_train1,]
y_test_geom1 = r.y_geom_1.iloc[ind_test1,]

kernel_init1 = gp.kernels.ConstantKernel(0.2)*gp.kernels.RBF(length_scale=0.05)
model_multiplegenes_geom1 = gp.GaussianProcessRegressor(kernel=kernel_init1, alpha=0.01, n_restarts_optimizer=5, optimizer = None, normalize_y=False)
model_multiplegenes_geom1.fit(x_train_geom1, y_train_geom1)
ypredicted_geom_1 = model_multiplegenes_geom1.predict(x_test_geom1)
avgerr_ideal_test_geom_1  = np.mean(ypredicted_geom_1  - y_test_geom1)
ytrain_geom_1 = model_multiplegenes_geom1.predict(x_train_geom1)
print(avgerr_ideal_test_geom_1)
#"fmin_l_bfgs_b"
```

```{python}
import numpy as np
import sklearn.gaussian_process as gp
from copy import deepcopy
import pandas as pd

trainsize2 = int(0.6*len(r.x_geom_2))
testsize2 = int(len(r.x_geom_2)-trainsize2)
indices2   = np.random.permutation(np.size(r.x_geom_2,axis=0))
ind_train2 = np.sort(indices2[0:trainsize2,])
ind_test2  = np.sort(indices2[testsize2:,])
x_train_geom2= r.x_geom_2.iloc[ind_train2,0:len(r.x_geom_2.columns)]
x_test_geom2 = r.x_geom_2.iloc[ind_test2,0:len(r.x_geom_2.columns)]
y_train_geom2= r.y_geom_2.iloc[ind_train2,]
y_test_geom2 = r.y_geom_2.iloc[ind_test2,]

kernel_init2 = gp.kernels.ConstantKernel(0.2)*gp.kernels.RBF(length_scale=0.05)
model_multiplegenes_geom2 = gp.GaussianProcessRegressor(kernel=kernel_init2, alpha=0.01, n_restarts_optimizer=5, optimizer = None, normalize_y=False)
model_multiplegenes_geom2.fit(x_train_geom2, y_train_geom2)
ypredicted_geom_2 = model_multiplegenes_geom2.predict(x_test_geom2)
avgerr_ideal_test_geom_2  = np.mean(ypredicted_geom_2  - y_test_geom2)
ytrain_geom_2 = model_multiplegenes_geom1.predict(x_train_geom2)
print(avgerr_ideal_test_geom_2)
#"fmin_l_bfgs_b"
```


We plot the results of the Gaussian Process Regression here. 
```{r message=FALSE, warning=FALSE}
ypredicted_geom_1 <- as.data.frame(py$ypredicted_geom_1)
ypredicted_geom_1$geometry <- "1"
names(ypredicted_geom_1) <- c("Y4", "Y5", "Y6", "Y7", "geometry")

ytrainpred_geom_1 <- as.data.frame(py$ytrain_geom_1)
ytrainpred_geom_1$geometry <- "1"
names(ytrainpred_geom_1) <- c("Y4", "Y5", "Y6", "Y7", "geometry")

ypredicted_geom_2 <- as.data.frame(py$ypredicted_geom_2)
ypredicted_geom_2$geometry <- "2"
names(ypredicted_geom_2) <- c("Y4", "Y5", "Y6", "Y7", "geometry")

ytrainpred_geom_2 <- as.data.frame(py$ytrain_geom_2)
ytrainpred_geom_2$geometry <- "1"
names(ytrainpred_geom_2) <- c("Y4", "Y5", "Y6", "Y7", "geometry")

yPredictedAll<-as.data.frame(bind_rows(ypredicted_geom_1, ypredicted_geom_2))

yTrainAll<-as.data.frame(bind_rows(ytrainpred_geom_1, ytrainpred_geom_2))

y_test_geom1 <- as.data.frame(py$y_test_geom1)
y_test_geom1$geometry <- "1"
names(y_test_geom1) <- c("Y4", "Y5", "Y6", "Y7", "geometry")
y_test_geom2 <- as.data.frame(py$y_test_geom2)
y_test_geom2$geometry <- "2"
names(y_test_geom2) <- c("Y4", "Y5", "Y6", "Y7", "geometry")
yTestAll<-as.data.frame(bind_rows(y_test_geom1, y_test_geom2))

yPredAllMelt <- as.data.frame(melt(yPredictedAll, value.name = "Predicted", variable.name = "Gene", id.vars=c("geometry")))
yTestAllMelt <- as.data.frame(melt(yTestAll[,2:3], value.name = "Actual", variable.name = "Gene2"))
yAllTestDataMelt <- cbind(yPredAllMelt, yTestAllMelt)

y_train_geom1 <- as.data.frame(py$y_train_geom1)
y_train_geom1$geometry <- "1"
names(y_train_geom1) <- c("Y4", "Y5", "Y6", "Y7", "geometry")
y_train_geom2 <- as.data.frame(py$y_train_geom2)
y_train_geom2$geometry <- "2"
names(y_train_geom2) <- c("Y4", "Y5", "Y6", "Y7", "geometry")
yTrainAll<-as.data.frame(bind_rows(y_train_geom2, y_train_geom2))

yTrainPredAllMelt <- as.data.frame(melt(yTrainAll, value.name = "Predicted", variable.name = "Gene", id.vars=c("geometry")))
yTrainAllMelt <- as.data.frame(melt(yTrainAll[,2:3], value.name = "Actual", variable.name = "Gene2"))
yAllTrainDataMelt <- cbind(yTrainPredAllMelt, yTrainAllMelt)


byActual <- yAllTrainDataMelt %>% group_by(Actual, Gene, geometry)

summaryTrainData <- byActual %>%
 summarise(
  count = n(),
  Predicted = median(Predicted, na.rm = TRUE),
  sd = sd(Predicted, na.rm = TRUE))


ggplot(yAllTestDataMelt, aes(x=Actual, y=Predicted, color = geometry)) +
   geom_point(size=3) + 
   geom_abline(color="red") + 
   geom_point(data=yAllTrainDataMelt, fun.y="median", col="black", alpha=0.5, shape=4, size=3) +
   coord_cartesian(xlim=c(-1,1), ylim=c(-1,1)) + 
   facet_wrap(~Gene) + theme_bw()
```

Accuracy of the GP models using the test set.
```{r}
print(paste0("Gene4 MAE using GP regression is (original data):", MAE(yTestAll$Y4, yPredictedAll$Y4)))
print(paste0("Gene5 MAE using GP regression is (original data):", MAE(yTestAll$Y5, yPredictedAll$Y5)))
print(paste0("Gene6 MAE using GP regression is (original data):", MAE(yTestAll$Y6, yPredictedAll$Y6)))
print(paste0("Gene7 MAE using GP regression is (original data):", MAE(yTestAll$Y7, yPredictedAll$Y7)))
```


Bayesian Optimization Scenario 2: perform a more extensive search involving ONLY ONE grid of topography parameters WITHOUT the empirical dataset. The assumption here is that the empirical data (presumably the result of a prior screening experiment) is used only as a model to predict the outcome of the unkwnon topographies. We use the same grid dataset here so we still only search within the limits!
```{r message=FALSE, warning=FALSE}
rm('bayesian_optimization_withgrid_iter2')
source_python('bayesian_optimization_real_withGrid3.py')

#set some parameters here
exp = 50
offset = 10

#import the gridToUse that you want to search through here
gridToUse <- data.matrix(read_csv(glue("grid_1.csv"))[2:3])

for(g in 1:2){
   geomData <- subset(allData, allData$Geometry_Number == g)
   x = as.data.frame(geomData[,7:8])
   yraw = as.data.frame(geomData[,14:17])
   ylog = log10(yraw)
   ymax = unlist(lapply(ylog, max))
   y = ylog/ymax
   
   allTopoToPcrGridMaxData_s4 <- NULL
   indexBayesOptMax <- NULL
   indexRndMax <- NULL
   

   for (num in 1:exp){
      all_ymax_bayesopt <- NULL
      all_ymax_rnd <- NULL
      active_ind_bayesopt <- NULL
      active_ind_rnd <- NULL
      all_experiment <- NULL
      all_iterations <- NULL
      predictedy_bayesopt <- NULL
      predictedy_rnd <- NULL
      holderBayesopt <- NULL
      holderRnd <- NULL
      y_best_bayesopt_iter <- NULL
      y_best_rnd_iter <- NULL
      holderIndexBayesOptMax <- NULL
      holderIndexRndMax <- NULL
      weightedBayesOpt <- NULL
      weightedRnd <- NULL
   
      set.seed(num*183+40)

      resToUse <- get(glue("res_geom{g}"))
      kern_bayesopt <- resToUse[[7]]
      kern_rnd <- get(glue("kernel_init{g}"))

      #choosing a random initialization point from the gridToUse
      ind_new_bayesopt = list(sample(1:nrow(gridToUse)-1, 1, replace=F))
      ind_new_rnd = list(sample(1:nrow(gridToUse)-1, 1, replace=F))
   
      testBayesOpt <- as.data.frame(t(gridToUse[ind_new_bayesopt[[1]]+1,1:2]))
      testRnd <- as.data.frame(t(gridToUse[ind_new_rnd[[1]]+1,1:2]))
      
      if(g == 1){
         holderBayesopt <- py$model_multiplegenes_geom1$predict(testBayesOpt)
         holderRnd <- py$model_multiplegenes_geom1$predict(testRnd)
      
      } else if(g==2){
         holderBayesopt <- py$model_multiplegenes_geom2$predict(testBayesOpt)
         holderRnd <- py$model_multiplegenes_geom2$predict(testRnd)
      }
      
      weightedBayesOpt <- as.data.frame(log10(10^(holderBayesopt[,1]*ymax[1]) + (10^(holderBayesopt[,2]*ymax[2]))*1.684 + (10^(holderBayesopt[,3]*ymax[3]))*2.939 + (10^(holderBayesopt[,4]*ymax[4]))*2.206))[,1]
      names(weightedBayesOpt) <- NULL
      weightedRnd <- as.data.frame(log10(10^(holderRnd[,1]*ymax[1]) + (10^(holderRnd[,2]*ymax[2]))*1.684 + (10^(holderRnd[,3]*ymax[3]))*2.939 + (10^(holderRnd[,4]*ymax[4]))*2.206))[,1]
      names(weightedRnd) <- NULL
            
      predictedy_bayesopt <- as.data.frame(weightedBayesOpt)
      predictedy_rnd <- as.data.frame(weightedRnd)
      
      all_ymax_bayesopt  <- predictedy_bayesopt
      all_ymax_rnd  <- predictedy_rnd
      all_experiment <- num
      active_ind_bayesopt <- ind_new_bayesopt
      active_ind_rnd <-ind_new_rnd
      all_iterations <- 0
      
      print(paste0("Experiment:", num))
      maxiter = nrow(gridToUse)-1
   
      for (i in 1:maxiter) {
   
            res_3  <- bayesian_optimization_withgrid_iter2(gridx = gridToUse, ally_bayesopt = predictedy_bayesopt, ally_rnd = predictedy_rnd, all_activeind_bayesopt = active_ind_bayesopt, all_activeind_rnd=active_ind_rnd, kernel_bayesopt=kern_bayesopt, kernel_rnd=kern_rnd, n_offset_bayesopt=offset, counter=i)
   
            ind_new_bayesopt  <- unlist(res_3[[3]])
            ind_new_rnd  <- unlist(res_3[[4]])
            y_best_bayesopt_iter  <- res_3[[5]]$values[1]
            y_best_rnd_iter  <- res_3[[6]]$values[1]
            kern_bayesopt  <- res_3[[7]]
            kern_rnd  <- res_3[[8]]
            all_ymax_bayesopt  <- rbind(all_ymax_bayesopt, y_best_bayesopt_iter)
            all_ymax_rnd  <- rbind(all_ymax_rnd, y_best_rnd_iter)
            all_experiment  <- rbind(all_experiment, num)
            all_iterations  <-  rbind(all_iterations, i)
            active_ind_bayesopt  <- rbind(active_ind_bayesopt, res_3[[3]])
            active_ind_rnd  <- rbind(active_ind_rnd, res_3[[4]])
            
            testBayesOpt <- as.data.frame(t(gridToUse[ind_new_bayesopt[[1]]+1,]))
            testRnd <- as.data.frame(t(gridToUse[ind_new_rnd[[1]]+1,]))
            
            if(g == 1){
               holderBayesopt <- py$model_multiplegenes_geom1$predict(testBayesOpt)
               holderRnd <-py$model_multiplegenes_geom1$predict(testRnd)
            
            } else if(g==2){
               holderBayesopt <- py$model_multiplegenes_geom2$predict(testBayesOpt)
               holderRnd <- py$model_multiplegenes_geom2$predict(testRnd)
            }
      
            weightedBayesOpt <- as.data.frame(log10(10^(holderBayesopt[,1]*ymax[1]) + (10^(holderBayesopt[,2]*ymax[2]))*1.684 + (10^(holderBayesopt[,3]*ymax[3]))*2.939 + (10^(holderBayesopt[,4]*ymax[4]))*2.206))[,1]
            names(weightedBayesOpt) <- NULL
            weightedRnd <- as.data.frame(log10(10^(holderRnd[,1]*ymax[1]) + (10^(holderRnd[,2]*ymax[2]))*1.684 + (10^(holderRnd[,3]*ymax[3]))*2.939 + (10^(holderRnd[,4]*ymax[4]))*2.206))[,1]
            names(weightedRnd) <- NULL
               
            predictedy_bayesopt <- rbind(predictedy_bayesopt, weightedBayesOpt)
            predictedy_rnd <- rbind(predictedy_rnd, weightedRnd)

            print(glue("Iteration: {i}, Experiment: {num}, Geometry: {g}"))
      }
         #does the data holder match the last data that we get?
         holderMaxData <- bind_cols(ymax_bayesopt = all_ymax_bayesopt, ymax_rnd = all_ymax_rnd, iterations = all_iterations, experiment = all_experiment, bayesopt_index = unlist(active_ind_bayesopt), predictedBayesOpt = predictedy_bayesopt, random_index = unlist(active_ind_rnd), predictedRnd = predictedy_rnd)
         holderMaxData$geometry <- g
         names(holderMaxData) <- c("ymax_bayesopt", "ymax_rnd", "iterations", "experiment", "bayesopt_index", "predictedBayesOpt", "random_index", "predictedRnd", "geometry")
         allTopoToPcrGridMaxData_s4 <- bind_rows(allTopoToPcrGridMaxData_s4, holderMaxData)
   
         holderIndexBayesOptMax <- rbind(holderIndexBayesOptMax,  min(which(holderMaxData$ymax_bayesopt == max(holderMaxData$ymax_bayesopt))))
         holderIndexBayesOptMax <- as.data.frame(holderIndexBayesOptMax)
         holderIndexBayesOptMax$geometry <- g
         indexBayesOptMax <- rbind(indexBayesOptMax, holderIndexBayesOptMax)
   
         holderIndexRndMax <- rbind(holderIndexRndMax,  min(which(holderMaxData$ymax_rnd == max(holderMaxData$ymax_rnd))))
         holderIndexRndMax <- as.data.frame(holderIndexRndMax)
         holderIndexRndMax$geometry <- g
         indexRndMax <- rbind(indexRndMax, holderIndexRndMax)

   }
   assign(glue("res_s4_geom{g}"), res_3)
   assign(glue("indexBayesOptMax_s4_geom{g}"), indexBayesOptMax)
   assign(glue("indexRndMax_s4_geom{g}"), indexRndMax)
   assign(glue("allTopoToPcrGridMaxData_s4_geom{g}"), allTopoToPcrGridMaxData_s4)
   write.csv(allTopoToPcrGridMaxData_s4, file=glue("allTopoToPcrGridMaxData_s4_geom{g}.csv"))
   write.csv(holderIndexBayesOptMax, file=glue("indexBayesOptMax_s4_geom{g}.csv"))
   write.csv(holderIndexRndMax, file=glue("indexRndMax_s4_geom{g}.csv"))
   
}

combinedGeom_allTopoToPcrGridMaxData_s4 <- rbind(allTopoToPcrGridMaxData_s4_geom1, allTopoToPcrGridMaxData_s4_geom2)
combinedGeom_allTopoToPcrGridMaxData_s4$ExptGeomCombo <- paste0(combinedGeom_allTopoToPcrGridMaxData_s4$geometry, sep="_", combinedGeom_allTopoToPcrGridMaxData_s4$experiment)
combinedGeom_allTopoToPcrGridMaxData_s4$ExptGeomComboArrange <- factor(combinedGeom_allTopoToPcrGridMaxData_s4$ExptGeomCombo, levels=c("1_1", "1_2", "1_3", "1_4", "1_5", "2_1", "2_2", "2_3", "2_4", "2_5"))

meltDataYmaxGrid_s4 <- melt(combinedGeom_allTopoToPcrGridMaxData_s4[c(1,2,3,9,11)], value.name = "ymax", variable.name = "type", id.vars=c("geometry", "ExptGeomComboArrange", "iterations"))

averageData_s4 <- meltDataYmaxGrid_s4 %>% 
    group_by(iterations, type, geometry) %>% 
    summarise(mean.value=mean(ymax), stdev.value = sd(ymax))

ggplot(averageData_s4, aes(x = iterations, y = mean.value, color = type)) + 
   facet_wrap(~geometry, scales = "free") +
   geom_errorbar(aes(ymin = mean.value - stdev.value, ymax = mean.value + stdev.value), alpha=0.5) + 
   geom_point() + 
   geom_line() +
   theme_bw() +
   labs(title="Bayesian Optimization for searching \n gridToUse of new topographies \n without the empirical dataset and \n using only one gridToUse for all experiments (Scenario 4) \n averaged across 50 iterations", 
        x = "Experiments (Number of topographies queried)", 
        y = "Maximum qPCR value")

```

How many experiments needed on average to obtain the osteogenic maximum?
```{r message=FALSE, warning=FALSE}
for (g in 1:2){
   averageDataSubset_s4 <- subset(averageData_s4, averageData_s4$geometry == g)
   yMaxIndex<-which(averageDataSubset_s4$mean.value==max(averageDataSubset_s4$mean.value))
   BayesOptMaxIndex <- averageDataSubset_s4[min(yMaxIndex[lapply(yMaxIndex, "%%", 2)!=0]), 1]
   RndMaxIndex <- averageDataSubset_s4[min(yMaxIndex[lapply(yMaxIndex, "%%", 2)==0]), 1]
   print(glue("Average Min iterations needed by Bayes Opt to get to optimum of geometry {g} is {BayesOptMaxIndex}"))
   print(glue("Average Min iterations needed by Rnd to get to optimum of geometry {g} is {RndMaxIndex}"))
}
```

What are the disorder and diamter of the topographies that maximize osteogenesis? 
```{r}

predictedgeom1_all_s4 <- NULL
predictedgeom2_all_s4 <- NULL

for(num in 1:exp){
   s4Subset_geom1 <- subset(allTopoToPcrGridMaxData_s4_geom1, allTopoToPcrGridMaxData_s4_geom1$experiment==num)
   s4Subset_geom2 <- subset(allTopoToPcrGridMaxData_s4_geom2, allTopoToPcrGridMaxData_s4_geom2$experiment==num)
   index_geom1 <- min(which(s4Subset_geom1$ymax_bayesopt == max(s4Subset_geom1$ymax_bayesopt)))-1
   index_geom2 <- min(which(s4Subset_geom2$ymax_bayesopt == max(s4Subset_geom2$ymax_bayesopt)))-1
   gridIndx_geom1 <- s4Subset_geom1[index_geom1,5]
   gridIndx_geom2 <- s4Subset_geom2[index_geom2,5]
   topo_geom1 <- gridToUse[gridIndx_geom1,]
   topo_geom2 <- gridToUse[gridIndx_geom2,]
   rescale_topo_geom1 <- bind_cols(Disorder = topo_geom1[1]*335.19+200, Diameter = topo_geom1[2]*736.36+811.11)
   rescale_topo_geom2 <- bind_cols(Disorder = topo_geom2[1]*221.81+129.09, Diameter = topo_geom2[2]*582.62+390.91)
  predictedgeom1_all_s4 <- rbind(predictedgeom1_all_s4, rescale_topo_geom1)
  predictedgeom2_all_s4 <- rbind(predictedgeom2_all_s4, rescale_topo_geom2)
}

print(glue("For HEX geometry, max topography have disorder {unique(predictedgeom1_all_s4[[1]])} and diameter {unique(predictedgeom1_all_s4[[2]])}"))
   print(glue("For SQ geometry, max topography have disorder {unique(predictedgeom2_all_s4[[1]])} and diameter {unique(predictedgeom2_all_s4[[2]])}"))

```

